### 2020-04-29 writeup/intro.tex
reorg

	Finally, we show that the transfer learning estimator always improves over mutli-task training.
		The amount of improvement becomes more significant as the model distance becomes larger.
		\item {\bf Covariate shift.} Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
		We provide fine-grained understanding on the amount of improvement that depends on covariate shift and data ratio.
		\item {\bf Data ratio.}
	\end{enumerate}

@@

>>>>

	Finally, we show that the transfer learning estimator always improves over mutli-task training.
		The amount of improvement becomes more significant as the model distance becomes larger.
		\item {\bf Covariate shift and data ratio.} Next we show that if we we only optimize the multi-task model on the target task, then we always obtain improved performance over single-task training.
		We provide fine-grained understanding on the amount of improvement that depends on covariate shift and data ratio.
	\end{enumerate}

@@

\subsection{Setup and Main Results}\label{sec_setup}

\paragraph{Data generation.}
In the multi-task learning (MTL) problem, we are given the input of $k$ tasks $(X_1, Y_1)$, $(X_2, Y_2)$, $\dots$, $(X_k, Y_k)$.
We shall assume that each task data follows a linear model.
For every $1\le i\le k$, we assume that
\[ Y_i = X_i \beta_i + \varepsilon_i, \]
where $\beta_i\in\real^p$ is the model parameter for the $i$-th task.
Each row of $X_i\in\real^{n_i\times p}$ is assumed to be drawn i.i.d. from a fixed distribution with covariance matrix $\Sigma_i$.
We assume that for every row $x$ of $X_i$, we have
\[ \ex{xx^{\top}} = \Sigma_i. \]
We also write $x = \Sigma_i^{1/2} z_i$, where $z_i$ is a random vector with mean $0$ and variance $1$.

\paragraph{The MTL problem.}
We use a shared body (module) $B\in\real^{p\times r}$ for all tasks and a separate head (module) $\set{W_i \in \real^{r}}_{i=1}^k$ for each task.
%    \paragraph{Different covariates:}
This corresponds to minimizing the following optimization objective.
\begin{align}
	\label{eq_mtl}
	f(B; W_1, \dots, W_k) = \sum_{i=1}^k \norm{X_i B W_i - Y_i}^2.
\end{align}
Note that we consider the natural parameterization without reweighting the tasks above.
The shared body $B$ plays an important role because it allows information transfer between different task data.
There are two ways to ensure the sharing of information between tasks.
\begin{itemize}
	\item Adding a regularization over $B$, e.g. \cite{LPTV09,LPVT11}.
	\item Controlling the capacity $r$ of $B$, e.g. \cite{KD12,WZR20}. Moreover, \cite{KD12} observed that controlling the capacity can outperform the implicit capacity control of adding regularization over $B$.
\end{itemize}
